Visualising CHD Pathway Inequalities by ethnicity - DRAFT

### 2024-04-18 draft_report.qmd
Adding IMD analysis of clustered practices

describe

@@

>>>>

Table 2 shows that the most diverse clusters are younger and the least diverse clusters are older. In particular almost one quarter of cluster 5 are under 18, compared to 19% of cluster 1 and 12% of cluster 1 are aged 75+ compared to only 4% of clusters 4 and 5.

@@

```{r}
source("R/get_imd_data_by_gpprac.R")

patientweighted_practice_imd |>
  mutate(gp_imd_quantile = case_when(gp_imd_decile<=2 ~ 1,
                                     gp_imd_decile==3 ~2,
                                     gp_imd_decile==4 ~2,
                                     gp_imd_decile==5 ~3,
                                     gp_imd_decile==6 ~3,
                                     gp_imd_decile==7 ~4,
                                     gp_imd_decile==8 ~4,
                                     gp_imd_decile>=9 ~5,
                                     .default = 0
  ))|>
  group_by(gp_imd_quantile,cluster)|>
  summarise(patients=sum(patients))|>
  gt()
```
